Notebook of learning from ensemble labels

### 2021-07-06 docs/notebook_learn_dl_ensemble.Rmd
Update catalogs

```
python hrlcm/fit_compose_lr.py --exp_name dpl_compose_lr --num_workers 32 --model deeplab --gpu_devices '0,1,2,3' --train_batch_size 16 --val_batch_size 16
```

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_da --num_workers 32 --gpu_devices '0,1,2,3' --save_freq 5 --resume1 'results/dl/unet_cot_da/model1_final.pth' --resume2 'results/dl/unet_cot_da/model2_final.pth'
```

>>>>

```
python hrlcm/fit_compose_lr.py --exp_name unet_single_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
```
